QueryMed: For Querying Biomedical Data on the Web\titlenote{Interested readers are advised to visit http://code.google.com/p/querymed to learn more about QueryMed.}

### 2010-11-20 docs/www2011/sigproc-sp.tex
made some other changes

\documentclass{acm_proc_article-sp}

\begin{document}

\title{QueryMed: An Intuitive Query Builder for Biomedical Data available on the Web}

@@

The quantity of publicly available data in the biomedical domain has dramatically increased over recent years. With the linked open data movement, the Semantic Web community has been very proactive in converting these rich information resources to RDF~\cite{LinkingData}.  The biomedical domain is among the early successes of the Semantic Web, due to the rapidity with which the community has made its data available in RDF triple stores~\cite{Yip}.  However, to allow end users to exploit the abundance of biomedical RDF data, there is a need for easy-to use systems that do not require the end user to have knowledge of the underlying  structure of the data, and that also allow them to run federated queries across multiple data sources.  There is also a  need for efficient hybrid interfaces that allow both browsing and querying data~\cite{Jentzsch}.

Answering many medically and biologically relevant questions requires searching, filtering, and combining information from multiple data sources.  For example, a physician may know her patient's personal information, symptoms, current medications, and genotype. She may wish to determine the patient's treatment plan and identify clinical trials for which the patient is eligible.  Although the physician has a single question--``based on the information I have about this patient, what is the best treatment plan and set of clinical trials available?"--there is no single data source that the physician can use to answer this question. The information that the physician needs must be gathered from numerous data sources such as Pubmed, DailyMed, Drugbank, LinkedCT, Diseasome,  and Gene Ontology \cite{Pubmed, DailyMed, Drugbank, LinkedCT, Diseasome, GO}. Her question must be broken up into discrete pieces that can be executed individually at one data source at a time.  Since the physician must search many data sources in order to find an answer to her single question, she requires a system that can automatically run queries over multiple data sources. Also, the physician may not know SPARQL syntax, the location of the SPARQL endpoints (i.e. data sources), or the structure of the ontologies used to describe the data in the endpoints. She is likely to want an intuitive way to query and to display the query results.  Developing intuitive ways to query multiple SPARQL endpoints and to display results is both an important and a challenging problem.  Our system, QueryMed, allows users with no knowledge of the SPARQL query language or the structure of the underlying ontologies to easily run queries across multiple SPARQL endpoints.

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{url}
\begin{document}

\title{QueryMed: For Querying Biomedical Data on the Web\titlenote{Interested readers are advised to visit http://code.google.com/p/querymed to learn more about QueryMed.}}

@@

Answering many medically and biologically relevant questions with information available on the Web requires searching, filtering, and combining information from multiple data sources.  For example, a physician who knows a patient's symptoms, current medications, and genotype may wish to determine the treatment plan and identify clinical trials for which the patient is eligible for.  However, there is no single data source that the physician can use to figure out the answers. The information that the physician needs must be gathered from numerous data sources such as Pubmed, DailyMed, Drugbank, LinkedCT, Diseasome,  and Gene Ontology \cite{Pubmed, DailyMed, Drugbank, LinkedCT, Diseasome, GO}. The quantity of publicly available data in the biomedical domain has dramatically increased over the recent years. With the linked open data movement, the Semantic Web community has been very proactive in converting these rich information resources to RDF~\cite{LinkingData}.  The biomedical domain is in fact among the early successes of the Semantic Web, due to the rapidity with which the community has made its data available in RDF triple stores~\cite{Yip}.  However, to exploit the abundance of this data on the Web, there is a need for easy-to-use systems that do not require the end-user to have knowledge of the underlying  structure of the data or the ontologies used in describing the data. These systems should also support the queries to be run across multiple data sources.  There is also a  need for efficient hybrid interfaces that allow both browsing and querying of data~\cite{Jentzsch}.

%Her question must be broken up into discrete pieces that can be executed individually at one data source at a time.  Since the physician must search many data sources in order to find an answer to her single question, she requires a system that can automatically run queries over multiple data sources. Also, the physician may not know SPARQL syntax, the location of the SPARQL endpoints (i.e. data sources), or the structure of the ontologies used to describe the data in the endpoints. She is likely to want an intuitive way to query and to display the query results.  Developing intuitive ways to query multiple SPARQL endpoints and to display results is both an important and a challenging problem.  Our system, QueryMed, allows users with no knowledge of the SPARQL query language or the structure of the underlying ontologies to easily run queries across multiple SPARQL endpoints.
